A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-13 6_validation.tex
more validation changes

\paragraph{Manufacturability}
Depending on the hardware configuration some bead widths are difficult to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
\todo{Tim should put pictures of extremal bead widths in introduction!}
We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.

\subsection{Experimentation}
\todo{Tim will print objects and show qualities:}
\begin{itemize}
\item visual consistency of flat top skin surface
\item visual gradual transparency changes
\item graphs of tensile tests on thin walled object
\end{itemize}

>>>>

\paragraph{Uniformity}
Depending on the hardware configuration some bead widths might be difficult to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
\todo{Include picture of flutter?}
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle,
which employs linear advance on a direct drive extruder for accurate deposition width control.
We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.

\todo{Maybe test the following qualities:}
\begin{itemize}
\item visual consistency of flat top skin surface
\item graphs of tensile tests on thin walled object
\end{itemize}
